The Mass Relations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGN Systems.

### 2020-03-13 manuscript/manuscript.tex
update paper draft
almost finished but need revise

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{H$_{\alpha}$}
\newcommand{\Hb}{H$_{\beta}$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}

@@

% Abstract of the paper
\begin{abstract}
Strong lensed AGN has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies. In this work, we have adopted eight strongly lensed system from the H0LiCOW collaboration. The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population. 
The \mbh\ are estimated using the board emission line. We compare our inference to the ones in the literature and find a consistent result. The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs. The sample of the data are supposed to increase rapidly.
\end{abstract}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution.

The origin of these relations is till unclear so far. In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection or having them share a common gas supply. On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe. It is crucial to extend the correlation studies to higher redshift and understand their evolution as a function of redshift. Recently, \citet{Ding2020} measured the scaling relations at redshift range of $1.2<z<1.7$ based on a sample of 32 AGNs using \hst/WFC3. Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge. In the following up work, \citet{Ding2020b} used the measurements of the high-$z$ AGNs and compare to numerical simulations including the hydrodynamic simulation MassiveBlackII (MBII) and a semi-analytic model (SAM). The tightness of the scaling relation at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations. A larger sample at higher redshift would be even more beneficial to confirm this scenario.

Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study (ref[Peng2006]), 
provided that the lens modelling is accurate. \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in H0LiCOW collaboration. This work has confirm the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. As a following up effort, \citet{Ding2017b} has applied the advanced techniques to two strongly lensed systems to study their \mbh-\lhost\ relations and obtained consistent results to the ones in the literature.

In this work, we aim to make progress by completing the analysis of the entire eight systems. We have developed an independent approach to achieve a one-step inference of the host photometry. We adopt the a set of extended modelling choices to assure the accuracy of our measurements. Moreover, we comparing our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross check. 3/8 of our objects have multi-band \hst\ imaging and we are able to infer their host color to assess an accurate inference of the stellar mass. The extended range of the eight systems would help us to make a direct comparison to the latest measurements by \citet{Ding2020}. We also adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.

This paper is organized as follows xxx. Zeropoint are defined in the AB systems. A Chabrier initial mass function (IMF) is employed consistently.

\section{Sample Selection}\label{sec:sample_select}
We adopt the eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information of the observational conditions of our eight systems are given in Table~\ref{data_set}. Besides the adopted filter shown therein, some systems also observed by \hst\ by different bands. As will shown in Section~\ref{sec:mstar}, the multi-band information enables us to apply the stellar population, hence a more accurate \mstar\ estimation.

While we note that our sample size included eight systems, which is a limited sample to constrain the evolution of the scaling relation. In this particular work, we simply aim to plot the scaling relation of our sample and make comparison to the ones in the literature. %[]The comparison sample (32 QSO paper)
We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 intermediate redshift QSO and 55 local measurements. It is worth noticing that they are so far the largest \hst\ imaging AGN samples with redshift range from 1.9 to the local.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN information.}\label{data_set}
\resizebox{9cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & $z$ & camera & Filter & exposure & pixel scale \\
 & & & & time (s) & (drizzled) \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & $0\farcs{}08$ \\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & $0\farcs{}05$ \\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & $0\farcs{}08$ \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & $0\farcs{}08$ \\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & $0\farcs{}08$ \\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & $0\farcs{}03$ \\
HS2209$+$1914 & 1.07 & WFC3-UVIS & F814W & 14238 & $0\farcs{}03$ \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & $0\farcs{}03$ \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The observational information is presented in~\citet{Ding2017a}.
\end{tablenotes}  
%\end{threeparttable}
\end{table}

To assure the validity of the comparison, we adopt a class of self-consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. For the overall systems, we adopt the following virial formalism:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with a\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
b\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
Having achieved a consistent cross-calibration, we adopt the board line information from the literature \citep{Sluse2012, Peng2006, Shen2011} to estimate the \mbh. The information are presented in Table~\ref{mbh}. The uncertainty of the \mbh\ are expected as $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of lensed \mbh\ estimates.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{ccccc}
        \hline
Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
SDSS1206 & \Mgii & 5632 & 45.61 & 8.88 \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
HS2209 & xxx & xxx & xxx &  xxx  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The reference for the board line information. For SDSS1206, we follow Birrer2018~ref[] and consider the magnification effect to correct the L.
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry with lensing technique}
We present the lensed host galaxy source reconstruction to derive their intrinsic photometry in this section. Our lensed AGN systems are from the H0LiCOW project, and the lens models of four systems have been derived with host galaxies reconstructed ref[]. Aiming at time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstruction of the host galaxy is only a by-product. In this paper, we apply the state-of-the-art lens modeling technique and dedicate to recovering the photometry of the host galaxy. As will show, approach would allow us to obtain a one-step host magnitude defined by \sersic\ profile, which is consistent to the definitions in the literature. %Furthermore, for cross check purpose, we compare our inference to the reconstructions by the previous works.

\subsection{Model Choice}
We carry out the fitting process to subtract the central AGN light, constrain the lens model, and reconstruct the host galaxy in the source plan, simultaneously.
For all the systems, we assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component. For single \sersic\ case, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in ref[] that this prior value would result in a consistent host magnitude inference as to fix n to its true value.}. The bright AGNs are unsolved and modelled by a scaled point spread function (PSF). We also joint the fitting of the AGN position to the center of its host.
 We adopt the elliptical Power-law model to describe the surface mass density of the deflector; an external shear component is also added.

We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task. We following the standard procedure as described by~\citet{Ding2020} to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are drizzled to a higher resolution by setting a Gaussian kernel; the adopted final resolution are listed in Table~\ref{data_set}. We then adopt the {\sc photutils} by Python to model the 2-D global background light using SExtractor algorithm. We then remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood; see Figure~\ref{fig:image_inference}.

For each lens system, we adopt different choices to perform the fitting. The distribution of the fitting inference are assumed to sufficiently cover the truth. We then apply a statistical measurement to weighting for the final inference and estimate the uncertainty level. The different choice of the fitting including the following.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is consider as the initial PSF to input to the fitting, which is considered as different choice.
\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To avoid any overfitting, we fix the slope values during the lens modelling with three optional value $[1.9, 2.0, 2.1]$.
\end{enumerate}

All in all, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting. After  all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value. Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020}. Since there is no obvious evidence of better perform between QSO mask or PSF iteration, we selected each top-4 fitting by these to choice and combining them equally to derive the final results and to evaluate the uncertainties.

\subsection{Photometry Inference}\label{sec:photometry}
In this subsection, we describe the details of the fitting for each systems and present our inference of the host galaxy photometry.

\subsubsection{HE0435}
The modeling is set up based on the descriptions in the last section. We select 5 isolated stars in this field initial PSFs to input to the fitting with in total of 60 fittings for this system. Based on the top-eight choices, we perform the weighting algorithm and measure the host-to-total flux ratio, host magnitude, effective radius and \sersic\ index. The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(5) columns.

The lens model inference based on the best-fit result for HE0435 is drawn in Figure~\ref{fig:image_inference}-(a). Not surprisingly, we note that the residual level reveals are appears to be larger than the ones as presented by Ken[] or Simon[]. This is due to the fact that the definition of the host galaxy in our models is a 2-D \sersic\ model which is relatively simple compare to the pixellated reconstruction technique by {\sc Glee} or the shapelet functions as adopted by \lenstronomy. The smooth feature of our model couldn't capture the clumps in the host of the star-forming regions, however, our model is more effective to derive the global host light as function of the \sersic\ which is consistent to measurements in the comparison sample.

As a cross check, we compare our host magnitude to the measurement in Ding+2017[], in which they model the reconstructed host galaxy as \sersic\ based on Galfit []. The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$, %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$. 
which is slightly fainter than our inference, i.e. $mag = 21.50 \pm 0.35$. The offset is within $1-\sigma$ level.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\hc}{$H_0$}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{H$_{\alpha}$}
\newcommand{\Hb}{H$_{\beta}$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}

@@

% Abstract of the paper
\begin{abstract}
Strong lensed AGN has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies. In this work, we have adopted eight strongly lensed system from the H0LiCOW collaboration. The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population. 
The \mbh\ are estimated using the board emission line. We compare our inference to the ones in the literature and find a consistent result. The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs. The number of the detection of the lensed AGNs are supposed to increase rapidly leave this topic with a bright future...
\end{abstract}

@@

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
\section{Introduction}
\todo{Check abbreviation}\\
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}. The origin of the scaling relations is till unclear so far. In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}. On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe~\citep{Peng2007, Jahnke2011, Hirschmann2010}.

It is crucial to extend the correlation studies to higher redshift to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}. Recently, based on a sample of 32 AGNs, \citet{Ding2020a} (hereafter, D20) measured the scaling relations at redshift range up to $1.2<z<1.7$ using \hst/WFC3. Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge. In a following up work, \citep{Ding2020b} compared their measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}. The tightness of the observed scaling relations at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations. Apparently, a larger sample at higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.

Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study~\citep{Peng2006}, provided that the lens modelling could be accurately derived. To test the fidelity of the modern lens modelling technique, \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration. This work verified that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. As a following up effort, \citet{Ding2017b} has applied the advanced techniques to two strongly lensed systems to study their \mbh-\lhost\ relations and obtained consistent results to the ones in the literature.

In this work, we aim to make progress by completing the analysis of the entire eight systems. We would adopt a new independent approach to achieve a one-step inference of the photometry of the eight lensed host galaxies. We adopt the a set of extended modelling choices to assure the accuracy of our measurements. We will compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check. Besides, 3/8 of our objects have available multi-band \hst\ imaging and we are able to infer their host color so as to assess an accurate inference of the stellar mass. We also adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample. The extended range of the eight systems would help us to make a direct comparison to the latest measurements by D20.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and their BH masses. In Section~\ref{sec:lens_model}, we describe our approach that designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry  to derive the stellar mass and the scaling relations to compare to the contrast sample in Section~\ref{sec:result}. The discussion and conclusions are drawed in Section~\ref{sec:diss&conc}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the entire sample consistently.

\section{Sample Selection}\label{sec:sample_select}
We adopt eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. We refer to ref[H0licow1 and Ding2017a] for the descriptions of these data. We summarized the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
For conciseness, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).

Based on the observational data of these eight systems, \citet{Ding2017a} has performed the extensive and realistic simulation exercise to understand the fidelity of the source reconstruction and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. Thus, this work is mainly based on the imaging data listed in Table~\ref{data_set}. Moreover, as will show in Section~\ref{sec:mstar}, 3/8 systems also have the multi-band \hst\ imaging data which  enables us to apply more accurate stellar population to estimate their \mstar.

While we note that the sample size by this work (i.e., eight systems) is quite limited. Rather than using them to constrain the evolution of the scaling relation, we simply derive their scaling relations so as to make a direct comparison to the recent efforts in D20, which includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}. It is worth noting that they are so far the largest \hst\ imaging AGN samples with redshift range up to $z\sim1.9$.

\begin{table*}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN observational details.}\label{data_set}
\resizebox{13cm}{!}{
     \begin{tabular}{cccccccc}
        \hline
Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale \\
 & & & & time (s) &&& (drizzled) \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ \\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ \\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ \\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$ \\
HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The observational information is also presented in~\citet{Ding2017a}. 
      \item $^a$: For HS2209, it is visited by \hst\ twice ({\it vis05} and {\it vis06}). The exposure time is thus given separately.
\end{tablenotes}  
%\end{threeparttable}
\end{table*}

To assure the validity of the comparison, we adopt a class of self-consistent recipes to estimate the \mbh\ of our sample. For the entire systems, we follow D20 and adopt the following virial formalism:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The board line information of our samples are adopted from the literature \citep{Sluse2012, Peng2006, Shen2011}. The \mbh\ measurement, together with the properties of the board-line are listed in Table~\ref{mbh}. The uncertainty of the \mbh\ are expected as $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{ccccc}
        \hline
Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
SDSS1206 & \Mgii & 5632 & 45.61$^a$ & 8.88 \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
HS2209 & xxx & xxx & xxx &  xxx  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\item Note: $-$ The reference for the board line information. \\
$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect.
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry with lensing technique}\label{sec:lens_model}
We perform the study of the lens modelling to reconstruct the photometry of the lensed host galaxies in this section. Our lens systems are a part of the H0LiCOW project, and the lens models of 4/8 systems, including HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019}, have been derived. Aiming at the strong lensing time-delay cosmography~\citet{Treu2016}, these works mainly focused on deriving the precise and accurate lens models, while the reconstruction of the reconstructed host galaxies for these works can be considered as a by-product. In this work, we apply the state-of-the-art lens modelling technique and perform an independent effort focusing on recovering the photometry of the host galaxy. As will show, our approach would allow us to obtain a one-step host magnitude as defined by \sersic\ surface brightness profile; thus our measurements would be more consistent to the ones in the literature. Furthermore, for the 4/8 systems which has been studied in H0LiCOW project, we will make comparison to understand the accuracy of our analysis.

\subsection{Data Preparation and Modelling Setup}
We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}. We then adopt the {\sc photutils} by Python to model the 2-D global background light using SExtractor algorithm based on {\sc photutils} by Python. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see Figure~\ref{fig:image_inference}.

We carry out the forward modelling process to constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy, simultaneously. For any extended objects including the lensing galaxy and source galaxy, we assume their photometry can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in~\citet{Ding2017a} that setting \sersic\ $n$ as this prior value would result in a consistent host magnitude inference compared to a prior with fixing $n$ to the truth.}. The bright AGNs are unsolved and modelled by a scaled point spread function (PSF). We also jointly fit the AGN position to the center of its host galaxy. We adopt the elliptical Power-law model to describe the surface mass density of the deflector; an external shear component is also added.

We employ the imaging modelling tool \lenstronomy~\citep{lenstronomy} to perform the fitting task. For each system, we adopt different modelling choices to perform the fitting. The distribution of the fitting inference by the overall choices are supposed to sufficiently cover the truth. We then apply a statistical measurement and perform weighting algorithm to derive the final inference and the uncertainty level. The different modelling choices are selected based on the following options:
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as a initial PSF choice to input to the fitting.
\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite (noise boost); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} (PSF iteration).
\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To mitigate the overfitting of the slope value, we fix it with three optional values $[1.9, 2.0, 2.1]$.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting. After all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value. Since there is no evidence of any better performance for the options between noise boost and PSF iteration, we selected top-4 fittings from both of them and combining these two options equally to derive the final results and to evaluate the uncertainties. The weighting algorithm is introduced by D20 defined as follows:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter literally means that it has to be larger than~$1$. If $\alpha<1$, introducing the $\alpha$ would have a side-effect because the relative likelihood between different the selected choices would be too close.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray} 
We aim to use this recipe to weight each choice based on their relative goodness of fit, while ensuring at least 8 (i.e., $4+4$) are used to capture the range of systematic uncertainties. Similar to Ding20, we also tested that our finally inference would not change significantly if we chose a different number of top ranked choices.

Finally, the value of host properties and the root-mean-square error (i.e., $\sigma$ level) would be calculated based on the weights of the 8 top ranked choices by:
\begin{eqnarray}
\label{eq:infer_value}
\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
\end{eqnarray} 
\begin{eqnarray}
\label{eq:infer_scatter}
\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
\end{eqnarray}

\subsection{Photometry Inference}\label{sec:photometry}
In this subsection, we describe the details of the fitting for each system and present the inference of the photometry of the host galaxy.
